Hierarchy Builder: algebraic~hierarchies made easy in Coq with Elpi

### 2020-04-25 hb.tex
fixing overfull hbox
more typesetting + clarifications about Appendix C

\supplement{Source code of the Coq package: \url{https://github.com/math-comp/hierarchy-builder}}
\keywords{Algebraic Hierarchy, Packed Classes, Coq, Elpi, Metaprogramming, $\lambda$Prolog}%TODO mandatory; please add comma-separated list of keywords

@@

As depicted in figure~\ref{fig:puzzle} we change again the hierarchy
by declaring a \coq{Ring_of_Monoid} \factory{}, that, from the user point of view,
will look indistinguishable from the old \coq{Ring_of_Monoid} \mixin{}
and hence grant backward compatibility between version V3 and version V1.

@@

We describe mathematical structures with three kinds of dependent records: mixins, classes, and structures.
As shown in section \ref{sec:example}, a \mixin{} gathers operators and axioms newly introduced by a structure.
As in \cite[section 2.4]{DBLP:conf/tphol/GarillotGMR09}\cite[section 2]{KSdraft}, a class record is parametrized by the carrier type \coq{(T : Type)} and gathers all the operators and axioms of a structure by assembling mixins, and a \coq{Structure type} (a record) bundles a carrier and its class instance, as follows.
\begin{coqcode}
Module Monoid.
Record axioms (T : Type) : Type :=
  Class { Monoid_of_Type_mixin : Monoid_of_Type T; }.
Structure type : Type := Pack { sort : Type; class : axioms sort; }.
End Monoid.
\end{coqcode}
The \coq{Monoid} module plays the role of a name space and forces us to write
qualified names such as \coq{Monoid.type}; as a consequence we can reuse the
same unqualified names for other structures, i.e., class and structure record
can always be named as \coq{axioms} and \coq{type} respectively.

@@

\subsection{Multiple inheritance}
In order to introduce multiple inheritance, we extend the hierarchy described in
section~\ref{subsec:v3} with the structure of semirings%, which is another
%intermediate structure between monoids and rings
as depicted in figure \ref{fig:puzzle_v4}. Semirings introduce the binary
multiplication operator \coq{mul} and its identity element \coq{one}.
The full code of this V4 is available in Appendix~\ref{sec:full-v4-code}.

@@

(* Builder arrow from top right to bottom left *)
HB.builders Context (A : Type) (f : Ring_of_AbelianGroup A).

>>>>

\supplement{Coq package source: \url{https://github.com/math-comp/hierarchy-builder}}
\keywords{Algebraic Hierarchy, Packed Classes, Coq, Elpi, Metaprogramming, $\lambda$Prolog}%TODO mandatory; please add comma-separated list of keywords

@@

As depicted in Figure~\ref{fig:puzzle} we change again the hierarchy
by declaring a \coq{Ring_of_Monoid} \factory{}, that, from the user point of view,
will look indistinguishable from the old \coq{Ring_of_Monoid} \mixin{}
and hence grant backward compatibility between version V3 and version V1.

@@

We describe mathematical structures with three kinds of dependent records: mixins, classes, and structures.
As shown in Section \ref{sec:example}, a \mixin{} gathers operators and axioms newly introduced by a structure.
As in \cite[Section 2.4]{DBLP:conf/tphol/GarillotGMR09}\cite[Section 2]{KSdraft}, a class record is parametrized by the carrier type \coq{(T : Type)} and gathers all the operators and axioms of a structure by assembling mixins, and a \coq{Structure type} (a record) bundles a carrier and its class instance, as follows.
\begin{coqcode}
Module Monoid.
Record axioms (T : Type) : Type :=
  Class { Monoid_of_Type_mixin : Monoid_of_Type T; }.
Structure type : Type := Pack { sort : Type; class : axioms sort; }.
End Monoid.
\end{coqcode}
The \coq{Monoid} module plays the role of a name space and forces us to write
qualified names such as \coq{Monoid.type}; as a consequence we can reuse the
same unqualified names for other structures, i.e., class and structure record
can always be named as \coq{axioms} and \coq{type} respectively.

@@

\subsection{Multiple inheritance}
In order to introduce multiple inheritance, we extend the hierarchy described in
Section~\ref{subsec:v3} with the structure of semirings %, which is another
%intermediate structure between monoids and rings
as depicted in Figure~\ref{fig:puzzle_v4}, and name it V4. Semirings introduce the
binary multiplication operator \coq{mul} and its identity element
\coq{one}.  For the sake of completeness, the full code of V4 is available in
Appendix~\ref{sec:full-v4-code}.

@@

(* Builder arrow from top right to bottom left in Fig. 2. *)
HB.builders Context (A : Type) (f : Ring_of_AbelianGroup A).
